\tool: Revisiting BadUSB with Type-C

### 2021-03-17 WOOT/Files/related_work.tex
JFA

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Although \ac{USB} 2.0 does not
support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
from the victim without permission. However, in JFA, this data exfiltration is not
combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
capability.

>>>>

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}.

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
JFA~\cite{JFC}, short for Juice Filming Attacks,
abuses this standard and monitoring victim's device utilizing \ac{USB} 2.0 protocol. Although JFA~\cite{JFC} could  exfiltrates video data from the victim without permission,  
there are two main limitation compared with \tool: 
\ding{183} JFA~\cite{JFC} can only exfiltrate video data under from victim's device, while \tool can control the victim's device at the same time as monitoring the screen. For example, when the victim forgets to lock the screen of his/her device, JFA can only captrue the static screen of the victim's device. However \tool can open the payment application by mouse, exfiltrate the payment QR code, and steal money by scanning the payment QR code.
\ding{182} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest devices supporting \ac{MHL} are released in 2015, a lack of support of \ac{MHL} limits the capabilities of JFA. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.
